Stabilization-Free Virtual Element Methods

### 2022-05-30 stabfreevem.tex
proofread section 1

Recently a stabilization-free linear virtual element method, based on a higher order polynomial projection of the gradient of virtual element functions, is devised for Poisson equation in two dimensions in \cite{BerroneBorioMarcon2021,BerroneBorioMarcon2022}, where the degree of polynomial used in projection depends on the number of vertices of the polygon. We refer to~\cite{DAltriMirandaPatrunoSacco2021} for a discussion on similar stabilization-free virtual element methods for plane elasticity problem.
The idea in \cite{BerroneBorioMarcon2021,BerroneBorioMarcon2022} is not easy to extend to construct higher order stabilization-free virtual element methods, and
the analysis is rather elaborate. 
This motives us to construct stabilization-free virtual element methods in arbitrary degree of polynomial and arbitrary dimension in a unified way.

The key to construct stabilization-free virtual element methods to find a finite-dimensional space $\mathbb{V}(K)$ and a projector $Q_K$ onto space $\mathbb{V}(K)$ such that
\begin{enumerate}[(C1)]
\item It holds the norm equivalence 
\begin{equation}\label{intro:gradVknormequiv} 
\|Q_{K}\nabla v\|_{0,K}\eqsim \|\nabla v\|_{0,K} \quad \forall~v\in V_k(K)
\end{equation}
on shape function space $V_k(K)$ of virtual elements;
\item The projection $Q_{K}\nabla v$ is computable based on the degrees of freedom (DoFs) of virtual elements for $v\in V_k(K)$.
\end{enumerate}
We can choose $Q_{K}$ as the $L^2$-orthogonal projector with respect to the inner product $(\cdot, \cdot)_K$. The norm equivalence \eqref{intro:gradVknormequiv} implies space $\mathbb{V}(K)$ should be sufficiently large compared with the virtual element space $V_k(K)$.
In standard virtual element methods, $Q_{k-1}^{K}\nabla v$ \cite{BeiraodaVeigaBrezziMariniRusso2016} or $\nabla\Pi_k^{K}v$ \cite{BeiraoBrezziCangianiManziniEtAl2013,BeiraoBrezziMariniRusso2014,AhmadAlsaediBrezziMariniEtAl2013,AyusodeDiosLipnikovManzini2016} are used, where $Q_{k-1}^{K}$ is the $L^2$-orthogonal projector onto the $(k-1)$th order polynomial space $\mathbb P_{k-1}(K; \mathbb{R}^d)$, and $\Pi_k^{K}$ is the $H^1$ projection operator onto the $k$th order polynomial space $\mathbb P_{k}(K)$.
While only
$$
\|Q_{k-1}^{K}\nabla v\|_{0,K}\lesssim \|\nabla v\|_{0,K}, \quad \|\nabla\Pi_k^{K}v\|_{0,K}\lesssim \|\nabla v\|_{0,K}
$$
hold
rather than the norm equivalence \eqref{intro:gradVknormequiv}, then the additional stabilization term is usually necessary to ensure the coercivity of the discrete bilinear form.
To remove the additional stabilization term, $\mathbb{V}(K)$ is taken as $\mathbb P_{l}(K; \mathbb{R}^d)$ with large enough $l$ even for the lowest order case $k=1$ in \cite{BerroneBorioMarcon2021,BerroneBorioMarcon2022,DAltriMirandaPatrunoSacco2021}, and virtual element space $V_k(K)$ is modified accordingly to make $Q_{l}^{K}\nabla v$ computable.
Instead, we employ $k$th order or $(k-1)$th order $H(\div)$-conforming macro finite elements as $\mathbb{V}(K)$ in this paper, and keep the virtual element space $V_k(K)$ as usual ones.

>>>>

Recently a stabilization-free linear virtual element method, based on a higher order polynomial projection of the gradient of virtual element functions, is devised for Poisson equation in two dimensions in \cite{BerroneBorioMarcon2021,BerroneBorioMarcon2022}, where the degree of polynomial used in projection depends on the number of vertices of the polygon. We refer to~\cite{DAltriMirandaPatrunoSacco2021} for a discussion on similar stabilization-free virtual element methods for plane elasticity problem.
The idea in \cite{BerroneBorioMarcon2021,BerroneBorioMarcon2022} is not easy to extend to construct higher order stabilization-free virtual element methods, and
the analysis is rather elaborate. 
This motivates us to construct stabilization-free virtual element methods in arbitrary degree of polynomial and arbitrary dimension in a unified way.

The key to construct stabilization-free virtual element methods is to find a finite-dimensional space $\mathbb{V}(K)$ and a projector $Q_K$ onto space $\mathbb{V}(K)$ such that
\begin{enumerate}[(C1)]
\item It holds the norm equivalence 
\begin{equation}\label{intro:gradVknormequiv} 
\|Q_{K}\nabla v\|_{0,K}\eqsim \|\nabla v\|_{0,K} \quad \forall~v\in V_k(K)
\end{equation}
on shape function space $V_k(K)$ of virtual elements;
\item The projection $Q_{K}\nabla v$ is computable based on the degrees of freedom (DoFs) of virtual elements for $v\in V_k(K)$.
\end{enumerate}
We can choose $Q_{K}$ as the $L^2$-orthogonal projector with respect to the inner product $(\cdot, \cdot)_K$. The norm equivalence \eqref{intro:gradVknormequiv} implies space $\mathbb{V}(K)$ should be sufficiently large compared with the virtual element space $V_k(K)$.
In standard virtual element methods, $Q_{k-1}^{K}\nabla v$ \cite{BeiraodaVeigaBrezziMariniRusso2016} or $\nabla\Pi_k^{K}v$ \cite{BeiraoBrezziCangianiManziniEtAl2013,BeiraoBrezziMariniRusso2014,AhmadAlsaediBrezziMariniEtAl2013,AyusodeDiosLipnikovManzini2016} are used, where $Q_{k-1}^{K}$ is the $L^2$-orthogonal projector onto the $(k-1)$th order polynomial space $\mathbb P_{k-1}(K; \mathbb{R}^d)$, and $\Pi_k^{K}$ is the $H^1$ projection operator onto the $k$th order polynomial space $\mathbb P_{k}(K)$.
While only
$$
\|Q_{k-1}^{K}\nabla v\|_{0,K}\lesssim \|\nabla v\|_{0,K}, \quad \|\nabla\Pi_k^{K}v\|_{0,K}\lesssim \|\nabla v\|_{0,K}
$$
hold
rather than the norm equivalence \eqref{intro:gradVknormequiv}, then the additional stabilization term is usually necessary to ensure the coercivity of the discrete bilinear form.
To remove the additional stabilization term, $\mathbb{V}(K)$ is taken as $\mathbb P_{l}(K; \mathbb{R}^d)$ with large enough $l$ even for the lowest order case $k=1$ in \cite{BerroneBorioMarcon2021,BerroneBorioMarcon2022,DAltriMirandaPatrunoSacco2021}, and the virtual element space $V_k(K)$ has to be modified accordingly to make $Q_{l}^{K}\nabla v$ computable.
Instead, we employ $k$th order or $(k-1)$th order $H(\div)$-conforming macro finite elements as $\mathbb{V}(K)$ in this paper, and keep the virtual element space $V_k(K)$ as usual ones.
